On Secure Delegation of SampBQP with a Classical Client

### 2019-11-27 hamiltonian.tex
Make editorial changes

In order to estimate the energy of a Hamiltonian using only $X$ and $Z$ measurements, the gates in the circle must be combinations of $X$ and $Z$ matrices. To begin, we apply a transformation to the circuit to use only real states and gates. This transform is taken from \cite{quant-ph/0301040}.

>>>>

Now we present a construction from \cite{quant-ph/0301040}.
